Meta-analysis

### 2019-10-31 05_MetaAnalysis.Rmd
Moving the import_data code to be above where it is used

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)
source("R/import_data.R")
```

@@

```{r data_import, message=FALSE, echo=FALSE}
PM_MB_means <- import_data()

@@

```{r rainfall_sum_Sstart}

source("R/Rainfall_x_cropYield.R")

# lm_rain <- read.csv("data/lmInSeasonRainfall_-10.20_50.110.csv",stringsAsFactors = FALSE)
# lm_rain <- read.csv("data/lmInSeasonRainfall_10.30_60.95.csv",stringsAsFactors = FALSE)
# lm_rain <- read.csv("data/lmInSeasonRainfall_20.40_80.110.csv",stringsAsFactors = FALSE)
# lm_rain <- read.csv("data/lmInSeasonRainfall_-10.30_50.80.csv",stringsAsFactors = FALSE)

>>>>

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)

@@

```{r data_import, message=FALSE, echo=FALSE}
source("R/import_data.R")
PM_MB_means <- import_data()

@@

```{r rainfall_sum_Sstart}
# The four data files were created from four scripts run as four jobs in Rstudio
# when the four jobs are finished they can be imported and combined into one data.frame
# source(Rainfall_x_cropYield_s-10.09_e30.65.R)
# source(Rainfall_x_cropYield_s-10.09_e65.100.R)
# source(Rainfall_x_cropYield_s10.30_e30.65.R)
# source(Rainfall_x_cropYield_s10.30_e65.10.R)

lm_rain1 <- read.csv("data/lmInSeasonRainfall_-10.09_30.64.csv",stringsAsFactors = FALSE)
lm_rain2 <- read.csv("data/lmInSeasonRainfall_-10.09_65.100.csv",stringsAsFactors = FALSE)
lm_rain3 <- read.csv("data/lmInSeasonRainfall_10.30_30.64.csv",stringsAsFactors = FALSE)
lm_rain4 <- read.csv("data/lmInSeasonRainfall_10.30_65.100.csv",stringsAsFactors = FALSE)

lm_rain <- rbind(lm_rain1,lm_rain2,lm_rain3,lm_rain4)
